Relationships in the extremes and their influence on competition and coexistence

### 2021-06-24 paper/Paper.Rnw
made some presentational errors, getting started fixing them. they have to do with the description of the general case.

For a general model, it is assumed that the growth rate $r_i(t)=\ln(N_i(t+1)/N_i(t))$ 
of species $i$ can be written as an increasing function of
an environment-dependent factor $E_i(t)$ and as a decreasing function of a quantity representing
competitive pressure on species $i$, $C_i(t)$. For simplicity, we here assume 
the $E_i(t)$ are iid through time, and likewise for the
$C_i(t)$. Though this assumption can be circumvented, we make the assumption because it simplifies the
presentation without obscuring main ideas. 
For the lottery model, we take $E_i(t)=B_i(t)$, henceforth assuming that fecundity depends strictly on
the environment. Competition, $C_i(t)$, in the lottery model is the number of new offspring
divided by the number of open sites, $C_i(t)=( B_1(t)N_1(t)+B_2(t)N_2(t) )/\delta N$, which
does not depend on $i$. Competition in the lottery model occurs at the stage of juveniles occupying open sites. 
Species growth rates for the lottery model can then be written 
$r_i(t)=\ln[1-\delta+E_i(t)/C_i(t)]=\ln[1-\delta+\delta N B_i(t)/(B_1(t)N_1(t)+B_2(t)N_2(t))]$.

In general, the storage effect for species $i$ is the contribution of covariation between $E_i(t)$ and 
$C_i(t)$ to a difference between invader and resident mean growth rates, when $i$ is the invader.
Specifically, storage effects for species $i$ are 
\begin{equation}
\Delta I_i = (\olr_{i\bs i} - q_{ij} \olr_{j \bs i})-(\olrs_{i \bs i}-q_{ij} \olrs_{j \bs i}),\label{eq:storage_effects_gen}
\end{equation}
where: $\olr_{i \bs i}$ refers to the mean ``invasion growth rate'' of species $i$, that is, the growth rate of 
species $i$ when it is at negligible abundance and species $j$ (the other species) is at stochastic steady state;
$\olr_{j \bs i}$ refers to the mean steady-state 
growth rate of species $j$ when species $i$ is absent (this is $0$, \emph{a priori});
and $\olrs_{i \bs i}$ and $\olrs_{j \bs i}$ are analogous quantities, but for an alternative model scenario, identical except that
the bivariate random variable $(E_i,C_i)$ has been replaced by a random variable $(E_i^\shp,C_i^\shp)$ 
with the same marginal distributions but independent components. The so-called \emph{scaling factor}
$q_{ij}$ measures the relative sensitivities to competition of the two species, see \cite{Chesson_1994},
\cite{Ellner_2016} and SI section \ref{SI-SIsect:scaling_factors} for the definition of $q_{ij}$, here 
omitted for brevity.

>>>>

For a general model, it is assumed that the growth rate $r_i(t)=\ln(N_i(t+1)/N_i(t))$ 
of species $i$ can be written as an increasing function of
an environment-dependent factor $E_i(t)$ and as a decreasing function of a quantity representing
competitive pressure on species $i$, $C_i(t)$. For simplicity, we here assume 
the $E_i(t)$ are iid through time, and likewise for the
$C_i(t)$. Though this assumption can be circumvented, we make the assumption because it simplifies the
presentation without obscuring ideas. 
For the lottery model, we take $E_i(t)=B_i(t)$, henceforth assuming that fecundity depends strictly on
the environment. Competition, $C_i(t)$, in the lottery model is the number of new offspring
divided by the number of open sites, $C_i(t)=( B_1(t)N_1(t)+B_2(t)N_2(t) )/\delta N$, which
does not depend on $i$. Competition in the lottery model occurs at the stage of juveniles occupying open sites. 
Species growth rates for the lottery model can then be written 
$r_i(t)=\ln[1-\delta+\delta N B_i(t)/(B_1(t)N_1(t)+B_2(t)N_2(t))]=\ln[1-\delta+E_i(t)/C_i(t)]$.

In general, the storage effect for species $i$ is the contribution of covariation between $E_i(t)$ and 
$C_i(t)$ to a difference between invader and resident mean growth rates, when $i$ is the invader.
Specifically, storage effects for species $i$ are 
\begin{equation}
\Delta I_i = (\olr_{i\bs i} - q_{ij} \olr_{j \bs i})-(\olrs_{i \bs i}-q_{ij} \olrs_{j \bs i}),\label{eq:storage_effects_gen}
\end{equation}
where: $\olr_{i \bs i}$ refers to the mean ``invasion growth rate'' of species $i$, that is, the growth rate of 
species $i$ when it is at negligible abundance and species $j$ (the other species) is at stochastic steady state;
$\olr_{j \bs i}$ refers to the mean steady-state 
growth rate of species $j$ when species $i$ is absent (this is $0$, \emph{a priori});
and $\olrs_{i \bs i}$ and $\olrs_{j \bs i}$ are analogous quantities, but for an alternative model scenario, identical except that
the influences of environment and competition in the invader and resident scenarios have been rendered independent.  
The so-called \emph{scaling factor}
$q_{ij}$ measures the relative sensitivities to competition of the two species, see \cite{Chesson_1994},
\cite{Ellner_2016} and SI section \ref{SI-SIsect:scaling_factors} for the definition of $q_{ij}$, here 
omitted for brevity.
